A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-01-29 report/proc.tex
booboo in bruno's adress
smalls changes to check

%%-----------------------------
%%      the top matter
%%-----------------------------
\title{A numerical study of the
	solution of X-Mode equations around the hybrid resonance}
\thanks{\rm The authors acknowledge 
	the support
	of ANR under contract ANR-12-BS01-0006-01. Moreover 
	this work was carried out within the framework of the European Fusion Development Agreement and 
	the French Research Federation for Fusion Studies. 
	It is supported by the European Communities under the contract of Association between Euratom and CEA. 
	The views and opinions expressed herein do not necessarily reflect those of the European Commission.} %\thanks{...}\thanks{...}% At most 5 thanks
%
\author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
\author{Bruno Despr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
\author{Lise-Marie Imbert-Gérard}\address{Courant Institute of Mathematical Sciences, New York University}
\author{Maryna Kachanovska}\address{POEMS, INRIA, ENSTA ParisTech, Paris}

@@

\begin{thebibliography}{99}
\bibitem{cedar}
Charles, F., Despr\'es, B., Merhenberg, M, 
Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal. 2013, 51(2), 840-863.

@@

\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.

@@

\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.

@@

\bibitem{Mouhot_2011} Mouhot, C., and Villani, C. (2011). On Landau damping. Acta mathematica, 207(1), 29-201.

\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
Handbook of mathematical functions
\end{thebibliography}

>>>>

%%-----------------------------
%%      the top matter
%%-----------------------------
\title{A numerical study of the
	solution of X-Mode equations around the hybrid resonance}
\thanks{\rm The authors acknowledge 
	the support
	of ANR under contract ANR-12-BS01-0006-01. Moreover 
	this work was carried out within the framework of the European Fusion Development Agreement and 
	the French Research Federation for Fusion Studies. 
	It is supported by the European Communities under the contract of Association between Euratom and CEA. 
	The views and opinions expressed herein do not necessarily reflect those of the European Commission.} %\thanks{...}\thanks{...}% At most 5 thanks
%
\author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
\author{Bruno Despr\'es}\address{Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7598, Laboratoire Jacques-Louis Lions, F-75005, Paris, France}
\author{Lise-Marie Imbert-Gérard}\address{Courant Institute of Mathematical Sciences, New York University}
\author{Maryna Kachanovska}\address{POEMS, INRIA, ENSTA ParisTech, Paris}

@@

\begin{thebibliography}{99}
	\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
	Handbook of mathematical functions
	\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
\bibitem{cedar}
Charles, F., Despr\'es, B., Merhenberg, M, 
Enhanced convergence estimates for semi-lagrangian schemes Application to the Vlasov-Poisson equation, SIAM J. Numer. Anal. 2013, 51(2), 840-863.

@@

@@

@@

\bibitem{Mouhot_2011} Mouhot, C., and Villani, C. (2011). On Landau damping. Acta mathematica, 207(1), 29-201.
\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
\bibitem{Xu_2006}Xu, L., ans Yuan, N. (2006). FDTD formulations for scattering from 3-D anisotropic magnetized plasma objects. Antennas and Wireless Propagation Letters, IEEE, 5(1), 335-338.
\end{thebibliography}

### 2015-01-29 report/timedomain.tex
smalls changes to check

\section{Time Dependent Problem Discretization}
Let us consider the system (\ref{eq:main_model}) in dimension one in the X-mode configuration which is transverse electric.
\subsection{A staggered scheme}
In this section, we develop a discretization of the time dependant problem~\eqref{eq:main_model} 
in one dimension. In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem, 
% \begin{align}
% \epsilon_0\partial_t E_{x}=-eN_e u_x, \nonumber\\
% \epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\nonumber\\
% \mu_0\partial_t H_z+\partial_x E_y-\partial_y E_x=0, \label{eq:tdpb}\\
% m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
% m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
% \end{align}
We compute a numerical approximation of~\eqref{eq:tdpb} on a cartesian grid using the Yee scheme, 
as suggested in \cite{stable_yee_plasma_current}. Let $n$ denote the time step index, as usual $t_n = n \Delta t$. 
It is standard (see \cite{Xu_2006,stable_yee_plasma_current }) to discretize the electrical field on the integer time step, 
\mrev{whereas the field $H_z$ is on half time steps, $t_{n+1/2}$}. The time discretization of the system reads:
 \bealn
 \left\{\begin{array}{l}
 \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}=-eN_e u_x, \nonumber\\
 \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z=-eN_e u_y,\nonumber\\
 \mu_0\frac{ H_z^{n+1/2}-H_z^{n-1/2}}{\Delta t}+\partial_x E_y-\partial_y E_x=0, \label{eq:tdiscretizedpb}\\
 m_e\frac{ u_{x}^{n+1}-u_x^{n}}{\Delta t}=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
 m_e\frac{u_{y}^{n+1}-u_y^{n}}{\Delta t}=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
\end{array}\right.
 \eealn
In Yee scheme, the differents components of the vector fields 
are defined on staggered points. 
We summarize this discretization on Fig.~\ref{schemepos} where the positions 
of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) 
on the discretized grid in space and time are shown. The fully discretized system then reads

>>>>

\section{Time Dependent Problem Discretization}
Let us consider the system (\ref{eq:main_model}) in dimension one in the X-mode configuration which is transverse electric.
\subsection{A staggered scheme}
In this section, we develop a discretization of the time dependant problem~\eqref{eq:main_model} 
in one dimension. In 1D, the derivatives with respect to $y$ vanish, and we are left with the following problem, 
% \begin{align}
% \epsilon_0\partial_t E_{x}=-eN_e u_x, \nonumber\\
% \epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\nonumber\\
% \mu_0\partial_t H_z+\partial_x E_y-\partial_y E_x=0, \label{eq:tdpb}\\
% m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
% m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
% \end{align}
We compute a numerical approximation of~\eqref{eq:main_model} on a cartesian grid using the Yee scheme, 
as suggested in \cite{stable_yee_plasma_current}. Let $n$ denote the time step index, as usual $t_n = n \Delta t$. 
It is standard (see \cite{Xu_2006,stable_yee_plasma_current }) to discretize the electrical field on the integer time step, 
whereas the field $H_z$ is on half time steps, $t_{n+1/2}$. The time discretization of the system reads:
 \bealn
 \left\{\begin{array}{l}
 \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}=-eN_e u_x, \nonumber\\
 \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z=-eN_e u_y,\nonumber\\
 \mu_0\frac{ H_z^{n+1/2}-H_z^{n-1/2}}{\Delta t}+\partial_x E_y-\partial_y E_x=0, \label{eq:tdiscretizedpb}\\
 m_e\frac{ u_{x}^{n+1}-u_x^{n}}{\Delta t}=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
 m_e\frac{u_{y}^{n+1}-u_y^{n}}{\Delta t}=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
\end{array}\right.
 \eealn
In Yee scheme, the differents components of the vector fields 
are defined on staggered points. 
We summarize this discretization on Fig.~\ref{schemepos} where the positions 
of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) 
on the discretized grid in space and time are shown. The fully discretized system then reads
